Data preparation

### 2020-09-09 production/prod_analysis-b.rmd
ajustes
* Se detecto el pais que sale al incorporar pib (Taiwan)
* Se arreglan modelos a los que le faltavan variables.
* Se agrega pib y redistribution en correlaciones
* Se compararon distintas maneras de calcular redistribucion (son equivalentes).
* Se ajustan graficos de spagetti
* Se ajustan pruebas de robustes a nuevos modelos (Aun hay un error que solucionar)
* Se mejora el orden de prep-data.
- Pendiente: Incorporar intro y metodo con llaves a paper.

graf2=ggpredict(results_2_redist_macro_bv, terms = c("merit","v5c [sample = 9]"), type="re")
pendiente_aleatoria_redistbv <- plot(graf2)
ggsave(pendiente_aleatoria_redistbv, filename = "output/results/pendiente_aleatoria_redistbv.png", width = 10, height = 10, dpi= "retina")

@@

results_3_redist_macro_bvi_interacgini_minmax <- sjPlot::plot_model(results_3_redist_macro_bvi, 
                                                                    type = c("int"), 
                                                                    title = "Interaccion desigualdad") +  scale_color_discrete("Gini Index", labels = c("Min", "Max")) + theme(legend.position = "bottom") + ylab("Redistributive preferences") + xlab("Meritocratic perception")

@@

```{r results='asis', cache=TRUE}
results_1_accum__1  = lmer(accum ~  gini_neto + fi_index + pibpc + 1 + (1| v5c), data = mer_pref, REML=F)
results_1_accum_3 = lmer(accum ~ merit + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_4 = lmer(accum ~  merit + bmerit + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_5 = lmer(accum ~  merit + bmerit + unmerit + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_6 = lmer(accum ~ merit + bmerit + unmerit + need + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_7 = lmer(accum ~ gini_neto + fi_index + merit + bmerit + unmerit + need + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_8 = lmer(accum ~ gini_neto + fi_index + merit + bmerit + unmerit + need + sstatus + as.factor(movstatus) + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_9 = lmer(accum ~ gini_neto + fi_index + merit + bmerit + unmerit + need + sstatus + as.factor(movstatus) + univ + as.factor(quintile_miss)  + sex + age  + 1 +  (1| v5c), data = mer_pref, REML=F)

@@

```{r, results='asis'}
htmlreg(list(results_1_accum__1, results_1_accum_3,results_1_accum_4,results_1_accum_5,results_1_accum_6,results_1_accum_7, results_2_accum_macro_bv, results_3_accum_macro_bvi), 
        caption = "Accumulation preferences models", 
        omit.coef = "(sstatus)|(movstatus)|(univ)|(quintile_miss)|(age)|(sex)", 
        custom.coef.names = c("Intercept", "Gini index" , "PIB per capita", "Economic freedom index", "Meritocratic perception", 
                              "Meritocratic preference", "Unmeritocratic Perception","Unmerit preference", "Economic-freedom Merit-perception"), 
        caption.above = T, 
        star.symbol = "\\*", 
        center = T, 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Since Model 6 control by subjetive status, mov subjetive status, Ed.univ, quintile_miss, age and sex") 
```

@@

ggsave(plot_grid(list(results_3_accum_macro_bvi_efect, pendiente_aleatoria_redistbv,mer_accum_int_f1, mer_accum_int_f2) ,
                 margin = c(0.5,0.5,0.5,0.5), tags = c(" ", " "," ", " ")), 
       filename = "output/results/results_3_accum_macro_bvi_interacgini.png", width = 10, height = 10, dpi= "retina")

@@

results_1_redist__1  = lmer(redist ~  gini_neto + fi_index + 1 + (1| v5c), data = mer_pref, REML=F)
results_1_redist_3 = lmer(redist ~ merit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_4 = lmer(redist ~  merit_g + bmerit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_5 = lmer(redist ~  merit_g + bmerit_g + unmerit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_6 = lmer(redist ~ merit_g + bmerit_g + unmerit_g + need_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_7 = lmer(redist ~ merit_g + fi_index + merit_g + bmerit_g + unmerit_g + need_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_9 = lmer(redist ~ gini_neto + fi_index + merit_g + bmerit_g + unmerit_g + need_g + sstatus + as.factor(movstatus) + univ + as.factor(quintile_miss)  + sex + age  + 1 +  (1| v5c), data = mer_pref, REML=F)
results_2_redist_macro_bv = lmer(redist ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g + gini_neto + fi_index + 1 +  (1 + merit| v5c), data= mer_pref, REML=F)
results_3_redist_macro_bvi = lmer(redist ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g + merit_g*gini_neto + fi_index + 1 +  (1 + merit_g | v5c), data = mer_pref, REML=F)

@@

```{r results='asis'} 
htmlreg(list(results_1_redist__1, results_1_redist_3,results_1_redist_4,results_1_redist_5,results_1_redist_6,results_1_redist_7, results_1_redist_9, results_2_redist_macro_bv, results_3_redist_macro_bvi),
        caption = "Redistributive preference models centered on the group mean", 
        omit.coef = "(sstatus)|(movstatus)|(univ)|(quintile_miss)|(age)|(sex)", 
        custom.coef.names = c("Intercept", "Gini index", "Economic freedom index", "Meritocratic perception", 
                              "Meritocratic preference", "Unmeritocratic Perception","Unmerit preference", "GINI x Merit-perception"), 
        caption.above = T, 
        star.symbol = "\\*", 
        center = T, 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Since Model 6 control by subjetive status, mov subjetive status, Ed.univ, quintile_miss, age and sex") 
```

@@

```{r results='asis', cache=TRUE}
results_1_accum__1  = lmer(accum ~  gini_neto + fi_index + 1 + (1| v5c), data = mer_pref, REML=F)
results_1_accum__2  = lmer(accum ~  gini_neto + fi_index + 1 + (1| v5c), data = mer_pref, REML=F)
results_1_accum_3 = lmer(accum ~ merit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_4 = lmer(accum ~  merit_g + bmerit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_5 = lmer(accum ~ merit_g + bmerit_g + unmerit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_6 = lmer(accum ~ merit_g + bmerit_g + unmerit_g + need_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_7 = lmer(accum ~ gini_neto + fi_index + merit_g + bmerit_g + unmerit_g + need_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_8 = lmer(accum ~ gini_neto + fi_index + merit_g + bmerit_g + unmerit_g + need_g + sstatus + as.factor(movstatus) + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_9 = lmer(accum ~ gini_neto + fi_index + merit_g + bmerit_g + unmerit_g + need_g + sstatus + as.factor(movstatus) + univ + as.factor(quintile_miss)  + sex + age  + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_macro = lmer(accum ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g + gini_neto + fi_index + 1 +  (1| v5c), data = mer_pref, REML=F)
results_2_accum_macro_bv = lmer(accum ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g +  gini_neto + fi_index + 1 +  (1 + merit_g| v5c), data = mer_pref, REML=F)
results_3_accum_macro_bvi = lmer(accum ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g +  gini_neto + merit_g*fi_index + 1 +  (1 + merit_g| v5c), data = mer_pref, REML=F)
results_3_accum_macro_bvi_2 = lmer(accum ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g +  fi_index + merit_g*gini_neto + 1 +  (1 + merit_g| v5c), data = mer_pref, REML=F)

@@

```{r, results='asis'}
htmlreg(list(results_1_accum__1,results_1_accum__2, results_1_accum_3,results_1_accum_4,results_1_accum_5,results_1_accum_6,results_1_accum_7, results_2_accum_macro_bv, results_3_accum_macro_bvi), 
        caption = "Accumulation preferences models centered on the group mean", 
        omit.coef = "(sstatus)|(movstatus)|(univ)|(quintile_miss)|(age)|(sex)", 
        custom.coef.names = c("Intercept", "Gini index", "Economic freedom index", "Meritocratic perception", 
                              "Meritocratic preference", "Unmeritocratic Perception","Unmerit preference", "Economic-freedom Merit-perception"), 
        caption.above = T, 
        star.symbol = "\\*", 
        center = T, 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Since Model 6 control by subjetive status, mov subjetive status, Ed.univ, quintile_miss, age and sex") 
```

>>>>

graf2=ggpredict(results_2_redist_macro_bv, terms = c("merit","v5c [sample = 9]"), type="re")
pendiente_aleatoria_redistbv <- plot(graf2)
pendiente_aleatoria_redistbv
ggsave(pendiente_aleatoria_redistbv, filename = "output/results/pendiente_aleatoria_redistbv.png", width = 10, height = 10, dpi= "retina")

@@

results_3_redist_macro_bvi_interacgini_minmax <- sjPlot::plot_model(results_3_redist_macro_bvi, 
                                                                    type = c("int"), 
                                                                    title = "Interaccion desigualdad", terms = c ("merit [-3,2]")) +  scale_color_discrete("Gini Index", labels = c("Min", "Max")) + theme(legend.position = "bottom") + ylab("Redistributive preferences") + xlab("Meritocratic perception")

@@

```{r results='asis', cache=TRUE}
results_1_accum__1  = lmer(accum ~  gini_neto + fi_index + pibpc + 1 + (1| v5c), data = mer_pref, REML=F)
results_1_accum_3 = lmer(accum ~ merit + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_4 = lmer(accum ~  merit + bmerit + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_5 = lmer(accum ~  merit + bmerit + unmerit + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_6 = lmer(accum ~ merit + bmerit + unmerit + need + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_7 = lmer(accum ~ gini_neto + fi_index + pibpc  + merit + bmerit + unmerit + need + 1 +  (1| v5c), data = mer_pref, REML=F)

results_1_accum_8 = lmer(accum ~ gini_neto + fi_index + merit + bmerit + unmerit + need + sstatus + as.factor(movstatus) + 1 +  (1| v5c), data = mer_pref, REML=F)

results_1_accum_9 = lmer(accum ~ gini_neto + fi_index + merit + bmerit + unmerit + need + sstatus + as.factor(movstatus) + univ + as.factor(quintile_miss)  + sex + age  + 1 +  (1| v5c), data = mer_pref, REML=F)

@@

```{r, results='asis'}
htmlreg(list(results_1_accum__1, results_1_accum_3,results_1_accum_4,results_1_accum_5,results_1_accum_6,results_1_accum_7, results_2_accum_macro_bv, results_3_accum_macro_bvi), 
        caption = "Accumulation preferences models", 
        omit.coef = "(sstatus)|(movstatus)|(univ)|(quintile_miss)|(age)|(sex)", 
        custom.coef.names = c("Intercept", "Gini index" , "Economic freedom index",  "PIB per capita" , "Meritocratic perception", 
                              "Meritocratic preference", "Unmeritocratic Perception","Unmerit preference", "Economic-freedom Merit-perception"),

        caption.above = T, 
        star.symbol = "\\*", 
        center = T, 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Since Model 6 control by subjetive status, mov subjetive status, Ed.univ, quintile_miss, age and sex") 
```

@@

ggsave(plot_grid(list(results_3_accum_macro_bvi_efect, pendientealeatoria_accum,mer_accum_int_f1, mer_accum_int_f2) ,
                 margin = c(0.5,0.5,0.5,0.5), tags = c(" ", " "," ", " ")), 
       filename = "output/results/results_3_accum_macro_bvi_interacgini.png", width = 10, height = 10, dpi= "retina")

@@

results_1_redist__1  = lmer(redist ~  gini_neto + fi_index + pibpc + 1 + (1| v5c), data = mer_pref, REML=F)
results_1_redist_3 = lmer(redist ~ merit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_4 = lmer(redist ~  merit_g + bmerit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_5 = lmer(redist ~  merit_g + bmerit_g + unmerit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_6 = lmer(redist ~ merit_g + bmerit_g + unmerit_g + need_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_7 = lmer(redist ~ gini_neto + fi_index + pibpc + merit_g + bmerit_g + unmerit_g + need_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_redist_9 = lmer(redist ~ gini_neto + fi_index + pibpc + merit_g + bmerit_g + unmerit_g + need_g + sstatus + as.factor(movstatus) + univ + as.factor(quintile_miss)  + sex + age  + 1 +  (1| v5c), data = mer_pref, REML=F)
results_2_redist_macro_bv = lmer(redist ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g + gini_neto + fi_index + pibpc + 1 +  (1 + merit| v5c), data= mer_pref, REML=F)
results_3_redist_macro_bvi = lmer(redist ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g + merit_g*gini_neto + fi_index + pibpc + 1 +  (1 + merit_g | v5c), data = mer_pref, REML=F)

@@

@@

```{r results='asis', cache=TRUE}
results_1_accum__1  = lmer(accum ~  gini_neto + fi_index + pibpc + 1 + (1| v5c), data = mer_pref, REML=F)
results_1_accum__2  = lmer(accum ~  gini_neto + fi_index + pibpc + 1 + (1| v5c), data = mer_pref, REML=F)
results_1_accum_3 = lmer(accum ~ merit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_4 = lmer(accum ~  merit_g + bmerit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_5 = lmer(accum ~ merit_g + bmerit_g + unmerit_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_6 = lmer(accum ~ merit_g + bmerit_g + unmerit_g + need_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_7 = lmer(accum ~ gini_neto + fi_index + pibpc  + merit_g + bmerit_g + unmerit_g + need_g + 1 +  (1| v5c), data = mer_pref, REML=F)
results_1_accum_8 = lmer(accum ~ gini_neto + fi_index + pibpc  + bmerit_g + unmerit_g + need_g + sstatus + as.factor(movstatus) + 1 +  (1| v5c), data = mer_pref, REML=F)

results_1_accum_9 = lmer(accum ~ gini_neto + fi_index + pibpc  + merit_g + bmerit_g + unmerit_g + need_g + sstatus + as.factor(movstatus) + univ + as.factor(quintile_miss)  + sex + age  + 1 +  (1| v5c), data = mer_pref, REML=F)

results_1_accum_macro = lmer(accum ~ univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g + gini_neto + fi_index + 1 +  (1| v5c), data = mer_pref, REML=F)

results_2_accum_macro_bv = lmer(accum ~ gini_neto + fi_index + pibpc + univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g +  gini_neto + fi_index + 1 +  (1 + merit_g| v5c), data = mer_pref, REML=F)

results_3_accum_macro_bvi = lmer(accum ~ gini_neto + fi_index + pibpc + univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g + merit_g*fi_index + 1 +  (1 + merit_g| v5c), data = mer_pref, REML=F)

results_3_accum_macro_bvi_2 = lmer(accum ~ gini_neto + fi_index + pibpc + univ + as.factor(quintile_miss) +	sstatus + as.factor(movstatus) + sex + age  + merit_g + bmerit_g + unmerit_g + need_g +  merit_g*gini_neto + 1 +  (1 + merit_g| v5c), data = mer_pref, REML=F)

@@

```{r, results='asis'}
htmlreg(list(results_1_accum__1, results_1_accum_3,results_1_accum_4,results_1_accum_5,results_1_accum_6,results_1_accum_7, results_2_accum_macro_bv, results_3_accum_macro_bvi), 
        caption = "Accumulation preferences models", 
        omit.coef = "(sstatus)|(movstatus)|(univ)|(quintile_miss)|(age)|(sex)", 
        custom.coef.names = c("Intercept", "Gini index" , "Economic freedom index",  "PIB per capita" , "Meritocratic perception", 
                              "Meritocratic preference", "Unmeritocratic Perception","Unmerit preference", "Economic-freedom Merit-perception"),

        caption.above = T, 
        star.symbol = "\\*", 
        center = T, 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Since Model 6 control by subjetive status, mov subjetive status, Ed.univ, quintile_miss, age and sex")
```

### 2020-09-09 production/prod_prep-data.rmd
ajustes
* Se detecto el pais que sale al incorporar pib (Taiwan)
* Se arreglan modelos a los que le faltavan variables.
* Se agrega pib y redistribution en correlaciones
* Se compararon distintas maneras de calcular redistribucion (son equivalentes).
* Se ajustan graficos de spagetti
* Se ajustan pruebas de robustes a nuevos modelos (Aun hay un error que solucionar)
* Se mejora el orden de prep-data.
- Pendiente: Incorporar intro y metodo con llaves a paper.

In diagram 1, a summary of the data processing is presented, which starts from international databases (input) to processed databases. As shown in the graph, the document is divided into 4 sections , corresponding to the subtitles of the codes.

In the first section, in addition to selecting and recoding ISSP variables, factor analyzes are performed to evaluate and create the latent variables of preferences about redistribution and inequality. In section 2, international SWIID and GOQ data are collected and added together with ISSP data, which includes predicted values for latent variables of meritocratic perceptions and preferences. In the next two sections, adjustments are made for multilevel analyzes for the pref.rda and meritocracy.rda databases.

@@

# Section-1: Preparation individual variables ISSP

## General preparation

@@

sjPlot::view_df(issp2009, max.len = 15)

@@

##  Preparation-data of the redistributive preference scales: redistrib.rda

@@

###  Rename & define object

@@

### Recode NAs

@@

### adjust labels NAs

@@

### Reverse code for SEM models

@@

### 2.4 Factor scores

@@

## Individual level variables: Sociodemograficas.

@@

### Recode sex
sjPlot::plot_frq(indepvar$sex, title ="Gender before")
indepvar$sex=ifelse(indepvar$sex==1,0,ifelse(indepvar$sex==2,1,NA))  
sjPlot::plot_frq(indepvar$sex, title ="gender after")

### Recode Age
  # Age
sjPlot::plot_frq(indepvar$age, title = "Age before",show.mean = T , show.values = F,show.n = F)

@@

sjPlot::plot_frq(indepvar$age_c, title = "Age after", show.na = T)

### Recode Education
sjPlot::plot_frq(indepvar$degree, coord.flip = TRUE, title = "Degree before")
  # Recode. Values over 5 are removed
indepvar$degree[indepvar$degree > 5]=NA

@@

sjPlot::plot_frq(indepvar$univ, coord.flip = TRUE, title = "Dummy university")

@@

stargazer(indepvar[1:41], type="html")

@@

knitr::kable(table(indepvar$movstatus), "html")

indepvar$movstatus[indepvar$movstatus>=8]= NA
indepvar$movstatus <- car::recode(indepvar$movstatus,recodes ="c(1,2)=2;3=1;c(4,5)=3;c(6,7)=4")
indepvar$movstatus <- set_labels(indepvar$movstatus,labels = c("Sin movilidad"=1,
                                                                    "Mov. Ascendente"=2,
                                                                    "Mov. Descendente"=3,
                                                                    "Indeterminado"=4))

knitr::kable(table(indepvar$movstatus), "html")
```

@@

## Measurement Merit & Getting ahead

@@

```{r}
#names(issp2009)
detearn = issp2009[, c("v47", "v48", "v49", "v50", "v51",
                       "v52", "v5", "id")]
names(detearn)
detearn$respons 	= detearn$v47
detearn$yeduc  	  = detearn$v48
detearn$family    = detearn$v49
detearn$child     = detearn$v50
detearn$welljob   = detearn$v51
detearn$hardjob   = detearn$v52
names(detearn)
detearn = detearn[-c(1:6)]
names(detearn)
# recode values 8 9 to NA
summary(detearn)
# freq(detearn$respons)
detearn[3:8][detearn[3:8] > 5] <- NA

@@

knitr::kable(summary(detearn), "html")

# Out Portugal (no answer in well job item)
detearn[which(detearn$v5 == 620), ] = NA
# adjust labels ###PROB PORTUCAL!!!
get_labels(detearn)
detearn[, 3:8][detearn[, 3:8] >= 8] <- NA
detearn$welljob <- sjlabelled::set_na(detearn$welljob, na = c(0))
knitr::kable(summary(detearn), "html")
# freq(detearn$welljob) ## prob portugal
detearn$welljob[detearn$welljob == 0] = NA
get_labels(detearn$welljob)
labels(detearn$welljob) = labels(detearn$respons)### PROB NOT SOLVED

@@

## Measuring Beliefs & Perceptions: merit_pref_perc

@@

# Section 2: agregar datos

@@

# Seccion 3:  add macro var

## Section 2.1: SWIID
```{r}
# Inequality swiid (4)        
#load(url("https://raw.githubusercontent.com/franciscomeneses/bases/master/swiid8_3.rda"))
load("input/data/original/swiid8_3.rda")

@@

## Section 2.2: Qog

@@

# Merge

@@

```{r}
mer_pref_polycor <- mer_pref %>% dplyr::select( 
"j_redist", "j_accum" , "j_merit","j_unmerit","j_bmerit","j_need",".dots...gini_disp",".dots...gini_mkt","fi_index")
save(mer_pref_polycor, file ="input/data/proc/mer_pref_polycor.rda")
```

# Pib per capita

@@

# Variable redistribución (Gini disminuido según impuestos y transferencias)

@@

>>>>

In the first section, in addition to selecting and recoding ISSP variables, factor analyzes are performed to evaluate and create the latent variables of preferences about redistribution and inequality. In section 2, international SWIID, GOQ and World bank data  are collected and added together with ISSP data, which includes predicted values for latent variables of meritocratic perceptions and preferences.

@@

# Section 1: Preparation individual variables ISSP

## 1.1 General preparation ISSP

 - change variable names to lowercase
 - Generate new sequential id individuals by country to merge

@@

@@

##  1.2 Preparation-data of the redistributive preference scales: redistrib.rda

@@

### 1.2.1 Preparation

- Rename & define object

@@

- Recode NAs

@@

- adjust labels NAs

@@

-  Reverse code for SEM models

@@

### 1.2.2 Factor scores

@@

## 1.3 Prepare individual level variables.

@@

### Recode sex
sex_plotbefore <- sjPlot::plot_frq(indepvar$sex, title ="Gender before")
indepvar$sex=ifelse(indepvar$sex==1,0,ifelse(indepvar$sex==2,1,NA))  
sex_plotafter <- sjPlot::plot_frq(indepvar$sex, title ="Gender after")

cowplot::plot_grid(sex_plotbefore, sex_plotafter, ncol=2)

### Recode Age
  # Age
agebefore<-sjPlot::plot_frq(indepvar$age, title = "Age before",show.mean = T , show.values = F,show.n = F, axis.labels = NULL)

@@

ageafter <- sjPlot::plot_frq(indepvar$age_c, title = "Age after", show.na = T, axis.labels =   c("18-25","25 -35", "35-45", "45-55", "55,65", "65-85","NA(>85)"))

cowplot::plot_grid(agebefore, ageafter, ncol=2)

### Recode Education
degrebefore <-sjPlot::plot_frq(indepvar$degree, coord.flip = TRUE, title = "Degree before")
  # Recode. Values over 5 are removed
indepvar$degree[indepvar$degree > 5]=NA

@@

degreafter<- sjPlot::plot_frq(indepvar$univ, coord.flip = TRUE, title = "Dummy university")

cowplot::plot_grid(degrebefore, degreafter, ncol=2)

@@

#stargazer(indepvar[1:41], type="html")

@@

movestatusbefore <- sjPlot::plot_frq(indepvar$movstatus, coord.flip = TRUE, title = "Subjective status mobility before")

indepvar$movstatus[indepvar$movstatus>=8]= NA
indepvar$movstatus <- car::recode(indepvar$movstatus,recodes ="c(1,2)=2;3=1;c(4,5)=3;c(6,7)=4")

indepvar$movstatus <- set_labels(indepvar$movstatus,labels = c("Sin movilidad"=1,
                                                                "Mov. Ascendente"=2,
                                                                    "Mov. Descendente"=3,
                                                                    "Indeterminado"=4))

movestatusafter <- sjPlot::plot_frq(indepvar$movstatus, coord.flip = TRUE, title = "subjective status mobility after")     
cowplot::plot_grid(movestatusbefore, movestatusafter, ncol=2)
```

@@

## 1.4 Measurement Merit & Getting ahead

@@

```{r}
#names(issp2009)
detearn = issp2009[, c("v47", "v48", "v49", "v50", "v51",
                       "v52", "v5", "id")]
#names(detearn)
detearn$respons 	= detearn$v47
detearn$yeduc  	  = detearn$v48
detearn$family    = detearn$v49
detearn$child     = detearn$v50
detearn$welljob   = detearn$v51
detearn$hardjob   = detearn$v52
#names(detearn)
detearn = detearn[-c(1:6)]
#names(detearn)
# recode values 8 9 to NA
#summary(detearn)
# freq(detearn$respons)
detearn[3:8][detearn[3:8] > 5] <- NA

@@

#knitr::kable(summary(detearn), "html")

# Out Portugal (no answer in well job item)
detearn[which(detearn$v5 == 620), ] = NA
# adjust labels ###PROB PORTUCAL!!!
#get_labels(detearn)
detearn[, 3:8][detearn[, 3:8] >= 8] <- NA
detearn$welljob <- sjlabelled::set_na(detearn$welljob, na = c(0))
#knitr::kable(summary(detearn), "html")
# freq(detearn$welljob) ## prob portugal
detearn$welljob[detearn$welljob == 0] = NA
#get_labels(detearn$welljob)
labels(detearn$welljob) = labels(detearn$respons)### PROB NOT SOLVED

@@

## 1.5 Measuring Beliefs & Perceptions: merit_pref_perc

@@

# Section 2: Multilevel preparation data.

@@

## 2.1: SWIID
```{r}
# Inequality swiid (4)        
#load(url("https://raw.githubusercontent.com/franciscomeneses/bases/master/swiid8_3.rda"))
load("input/data/original/swiid8_3.rda")

@@

```{r}
mer_pref$redis_bradley  <- as.numeric((1- mer_pref$gini_neto / mer_pref$gini_mkt) *100)
hist(mer_pref$redis_bradley)
```

## 2.2: Qog

@@

- Merge

@@

## Pib per capita

@@

Taiwán no posee información sobre pibpc en el banco mundial, por ende los casos de este pais son excluidos.

@@

```{r}
#mer_pref_polycor <- mer_pref %>% dplyr::select( 
#"j_redist", "j_accum" , #"j_merit","j_unmerit","j_bmerit","j_need",".dots...gini_disp",".dots...gini_mkt","fi_index", #"pibpc", "redis_relativo")
#save(mer_pref_polycor, file ="input/data/proc/mer_pref_polycor.rda")
```
